A Survey of Possible Exoskeleton Control Architectures and Algorithms\\ (Draft 3.1)

### 2015-09-25 control.tex
cga updates

\title{A Survey of Possible Exoskeleton Control Architectures and
Algorithms\\
(Draft 3.0)}

@@

I have incorporated your suggestions about robustness and underactuation
in the white paper
www.cs.cmu.edu/~cga/exo/control.pdf

>>>>

\title{A Survey of Possible Exoskeleton Control Architectures and
Algorithms\\
(Draft 3.1)}

@@

I have incorporated your suggestions about robustness and underactuation
in the white paper draft 3.1 now at:
www.cs.cmu.edu/~cga/exo/control.pdf
